Researchers' perceptions of malaria eradication: findings from a mixed-methods analysis of a large online survey

### 2018-04-07 paper.Rmd
removing formula

In other words, the rational assignment of resources for malaria eradication campaigns hinges on the expected value of those campaigns. We can describe this relationship below:

\begin{center}
$I_{T}$ = $P(x)_{}$ $\dfrac{B(m_{}*p)}{m_{}*p}$(1 + $\delta$)$^{-T}$ -  $P(x)_{}$ $\dfrac{C(m_{}*p)}{m_{}*p}$ (1 + $\delta$)$^{-T}$
\end{center}

\begin{itemize}
\item $ I $ is the return on investment
\item $ m $ is the prevalence of malaria
\item $ p $ is the population size
\item $ x $ is whether eradication has been achievied
\item $ T $ is the time-frame (to both costs and benefits)
\item $ P $ is the probability (of eradication)
\item $ B $ is the benefit of preventing malaria
\item $ C $ is the cost of preventing malaria
\item $ \delta $ represents both the discount rate and opportunity cost
\end{itemize}

(I) is the return on investment at time (T) (the "end of malaria"). We take the present value of the benefits multiplied by the probability of succcess minus the value of costs times the probability of success, and multiplyboth terms by the discount rate traised to T to arrive at the return on investment.

>>>>

In other words, the rational assignment of resources for malaria eradication campaigns hinges on the expected value of those campaigns, the latter being a direct function of the discount rate applied to future benefits (which this study does not aspire to assess) and the probability of "success" (ie, eradication). Holding constant factors such as the cost of eradication and the benefits of achieving it, the return on investment is a linear function of eradication's probability. Given this, estimating probability is crucial to evaluating if and when attempts at eradication should be undertaken.
